An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-04-20 poly-embed-journal/poly-embed-journal.tex
Refactoring section 5 statements: nonredundancy for set to for loss/property

\begin{definition}[Non-redundancy]\label{def:nonredundant}
	A report $r \in \R$ is \emph{redundant} for the discrete loss $\ell : \R \to \reals_+^\Y$ if $r$ does not uniquely optimize $\inprod{p}{\ell(\cdot)}$ for any $p \in \simplex$.
	A set $\R$ is called \emph{non-redundant} if it contains no redundant reports.
\end{definition}

\begin{definition}[Tight embedding]\label{def:tight-embedding}
	We say that a loss $L : \reals^d \to \reals_+^\Y$ \emph{tightly embeds} a discrete loss $\ell : \R \to \reals_+^\Y$ via the injection $\varphi :\R \to \reals^d$ if $L$ embeds $\ell$ and $\R$ is non-redundant.
\end{definition}

\begin{definition}[Trim]\label{def:trim}
	Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \text{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$ as the set of maximal level sets of $\Gamma$.
\end{definition}

\begin{proposition}\label{prop:nonredundant-iff-trim}
	Suppose $L$ elicits $\Gamma$.
	If a  set $\R$ is non-redundant for $L$ then $\{\Gamma_r \mid r \in \R\} = \trim(\Gamma)$.
\end{proposition}
\begin{proof}
	\jessie{Not an iff because you can have duplicate reports, which is consolidated by trim}
	If $\R$ is non-redundant, then every $r \in \R$ uniquely optimizes $L$ for some $p_r \in \simplex$.
	First, we have $\trim(\Gamma) \subseteq \{\Gamma_r \mid r \in \R\}$ trivially.
	Consider $r \in \R$.
	Since there is a $p_r \in \simplex$ so that$\Gamma(p_r) = \{r\}$.
	Therefore, we cannot have $\Gamma_r \subseteq \Gamma_{r'}$ for any other $r' \neq r \in \R$, and therefore $\Gamma_r \in \trim(\Gamma)$.
\end{proof}

\begin{proposition}\label{prop:min-rep-iff-trim}
	Suppose $L$ elicits $\Gamma$.
	If a  set $\R$ is a finite minimum representative set then $\{\Gamma_r \mid r \in \R\} = \trim(\Gamma)$.
\end{proposition}
\begin{proof}
	\jessie{Not an iff because you can have duplicate reports, which is consolidated by trim}
\end{proof}

\begin{corollary}
	$\R$ is non-redundant for $L$ if and only if $\R$ is a minimum representative set for $L$.
\end{corollary}

@@

\jessie{TODO: Relate to trim}

>>>>

\begin{definition}[Non-redundancy]\label{def:nonredundant}
A loss $\L : \R \to \reals^\Y_+$ eliciting $\Gamma:\simplex \toto \R$ is \emph{redundant} if there are reports $r, r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$, and \emph{non-redundant} otherwise.
\end{definition}

%\begin{definition}[Non-redundancy]\label{def:nonredundant}
%	A report $r \in \R$ is \emph{redundant} for the discrete loss $\ell : \R \to \reals_+^\Y$ if $r$ does not uniquely optimize $\inprod{p}{\ell(\cdot)}$ for any $p \in \simplex$.
%	A set $\R$ is called \emph{non-redundant} if it contains no redundant reports.
%\end{definition}

\begin{definition}[Tight embedding]\label{def:tight-embedding}
	We say that a loss $L : \reals^d \to \reals_+^\Y$ \emph{tightly embeds} a discrete loss $\ell : \R \to \reals_+^\Y$ via the injection $\varphi :\R \to \reals^d$ if $L$ embeds $\ell$ and $\ell$ is non-redundant.
\end{definition}

\begin{definition}[Trim]\label{def:trim}
	Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$ as the set of maximal level sets of $\Gamma$.
\end{definition}

Observe that if a loss $L : \R \to \reals_+^\Y$ eliciting the property $\Gamma : \simplex \toto \R$ is non-redundant, then $\{\Gamma_r \mid r \in \R\} = \trim(\Gamma)$ by applying the definition of non-redundancy.

%\begin{proposition}\label{prop:nonredundant-iff-trim}
%	Suppose $L$ elicits $\Gamma$.
%	If a  set $\R$ is non-redundant for $L$ then $\{\Gamma_r \mid r \in \R\} = \trim(\Gamma)$.
%\end{proposition}
%\begin{proof}
%	\jessie{Not an iff because you can have duplicate reports, which is consolidated by trim}
%	If $\R$ is non-redundant, then every $r \in \R$ uniquely optimizes $L$ for some $p_r \in \simplex$.
%	First, we have $\trim(\Gamma) \subseteq \{\Gamma_r \mid r \in \R\}$ trivially.
%	Consider $r \in \R$.
%	Since there is a $p_r \in \simplex$ so that$\Gamma(p_r) = \{r\}$.
%	Therefore, we cannot have $\Gamma_r \subseteq \Gamma_{r'}$ for any other $r' \neq r \in \R$, and therefore $\Gamma_r \in \trim(\Gamma)$.
%\end{proof}

\begin{proposition}\label{prop:min-rep-implies-trim}
	Suppose $L$ elicits $\Gamma$.
	If the set $\R$ is a finite minimum representative set for $L$, then $\{\Gamma_r \mid r \in \R\} = \trim(\Gamma)$.
\end{proposition}
\begin{proof}
We trivially have $\trim(\Gamma) \subseteq \{\Gamma_r \mid r \in \R\}$, so the other directino of inclusion is what's left to show.
For $r \in \R$, we want to show $\Gamma_r \in \trim(\Gamma)$.

\jessie{Implicit lemma about 3 ways to be redundant used here.}
We proceed in three cases: if there is not an $r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$, then $L$ is non-redundant.
If there is an $r'$ such that $\Gamma_r = \Gamma_{r'}$, $\R$ being a minimum representative set implies $r = r'$.
If there is an $r'$ such that $\Gamma_r \subsetneq \Gamma_{r'}$, then $\R \setminus \{r\}$ is also a representative set, so we contradict $\R$ being a minimum representative set.
Therefore, $\Gamma_r \in \trim(\Gamma)$.
\end{proof}

\begin{proposition}
	Let $L : \R' \to \reals^\Y_+$ be a given loss function and $\R$ a representative set for $L$.
	$L|_\R$ is non-redundant $\iff \R$ is a minimum representative set for $L$.
\end{proposition}
\begin{proof}
	$\implies$ If $L|_\R$ is non-redundant, then for any $r \in \R$, we want to show there exists a $p \in \simplex$ such that $\Gamma(p) \cap \R \setminus \{r\} = \emptyset$.
	By non-redundancy, we know there is no $r'$ such that $\Gamma_r \subseteq \Gamma_{r'}$.
	Therefore, if $r' \in \Gamma(p) \cap \R \setminus \{r\}$, we must still have some $p' \in \simplex$ so that $r' \not \in \Gamma(p')$.
	In particular, we claim that $\Gamma(p') \cap \R \setminus \{r\} = \emptyset$. \jessie{Prove this claim!}

	$\impliedby$
	We show the contrapositive: if $L|_\R$ is redundant, then $\R$ is not a minimum representative set for $L$.
	In particular, there is a pair, $r, r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$, and we can thus verify $\Gamma(p) \cap \R \setminus \{r\}$ is also a representative set.
	Therefore, $\R$ is not a minimum representative set.
\end{proof}

@@
